---
title: ANU Programs
date-modified: today
format: 
  html: default
execute:
  echo: false
  warning: false
---

```{r setup}
library(tidyverse)
library(visNetwork)
library(rvest)
targets::tar_source()
targets::tar_load_everything()
```

```{css}
.cell-output-display {
  border: 1px solid black;
}
```

The code for this document is avalable at <https://github.com/anuopensci/anu-programs>.

::: callout-note

## How to read the interactive network graph

- The **node** represents a course as indicated by the 4 letter alpha code followed by 4 digits
- The **edges** show the prerequisite required for the course.
- The **color** of nodes are such that:
  - blue are courses listed in the study options 
  - yellow are required but not listed in the study options
  - red are courses that don't seem to exist anymore
- You can **zoom** in to see more information.
- **Clicking** on the node takes you to the ANU course homepage.
- **Hovering** over the node displays the course name.

:::

## [Master of Statistics](https://programsandcourses.anu.edu.au/2024/program/MSTAT)

```{r}
program_study_table("MSTAT") 
```

```{r}
plot_network(mstat_courses, mstat_required) 
```

## [Master of Statistical Data Analysis](https://programsandcourses.anu.edu.au/2024/program/MSDA)



```{r}
plot_network(msda_courses, msda_required) 
```


## [Master of Applied Data Analytics](https://programsandcourses.anu.edu.au/program/madan)

```{r}
program_study_table("MADAN") 
```

```{r}
plot_network(madan_courses, madan_required) 
```

## [Bachelor of Applied Data Analytics](https://programsandcourses.anu.edu.au/program/BADAN)


## [Bachelor of Finance, Economics and Statistics (Honours)](https://programsandcourses.anu.edu.au/program/AFEST)

## [Bachelor of Statistics](https://programsandcourses.anu.edu.au/program/BSTAT)